\textbf{{\Large {Recursive algorithms, branching coefficients affine algebras and applications}}}

### 2010-03-16 AffineLieAlgebras/InformalNotes/article.tex
More work on affine semisimple Lie algebras

The set $\Delta^{+}_{\bot}$ is empty. 
\begin{enumerate}
\item Construct the set $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of the $\mathfrak{g}$-module $L^{(\mu)}$.
\item Select the weights $\left\{ \lambda=\omega(\mu+\rho) | \pi_{\mathfrak{a}_{\bot}}\lambda \in \bar{C}_{\mathfrak{a}_{\bot}} \right\}$ Since we have constructed the set $\Delta^{+}_{\bot}$ we can easily check wether the weight $\pi_{\mathfrak{a}_{\bot}}\lambda$ lies in the main Weyl chamber of $\mathfrak{a}_{\bot}$ by computing the scalar product of $\lambda$ with the roots of $\Delta^{+}_{\bot}$ that must be non-negative.
\item For $\lambda=\omega(\mu+\rho),\; \pi_{\mathfrak{a}_{\bot}}\lambda\in \bar{C}_{\mathfrak{a}_{\bot}}$ calculate the dimensions of the corresponding modules $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$ using the Weyl formula with the set $\Delta^{+}_{\bot}$.
\item Construct the set $\Gamma$ \eqref{fan-defined}.
\item Calculate the anomalous branching coefficients in the main Weyl
  chamber of the subalgebra $\mathfrak{a}$ using recurrent relation (\ref{recurrent-relation}).
\end{enumerate}

We limit our computation by the fifth grade.
The set of the anomalous weights of the representation of the algebra $\hat{A}_3$ consists of 192 elements.

>>>>

The set $\Delta^{+}_{\bot}$ is empty.

We limit our computation by the fifth grade.
The set  $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of the representation of the algebra $\hat{A}_3$ consists of 192 elements and its projection $\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ for $\mu=\omega_1$ is shown at the Figure. We omit similar pictures for $\omega_0, \omega_2,\omega_3$ and include only the branching coefficients for these modules to save the space.

\begin{enumerate}
\item Construct the set $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of the $\mathfrak{g}$-module $L^{(\mu)}$.
\item Select the weights $\left\{ \lambda=\omega(\mu+\rho) | \pi_{\mathfrak{a}_{\bot}}\lambda \in \bar{C}_{\mathfrak{a}_{\bot}} \right\}$ Since we have constructed the set $\Delta^{+}_{\bot}$ we can easily check wether the weight $\pi_{\mathfrak{a}_{\bot}}\lambda$ lies in the main Weyl chamber of $\mathfrak{a}_{\bot}$ by computing the scalar product of $\lambda$ with the roots of $\Delta^{+}_{\bot}$ that must be non-negative.
\item For $\lambda=\omega(\mu+\rho),\; \pi_{\mathfrak{a}_{\bot}}\lambda\in \bar{C}_{\mathfrak{a}_{\bot}}$ calculate the dimensions of the corresponding modules $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$ using the Weyl formula with the set $\Delta^{+}_{\bot}$.
\item Construct the set $\Gamma$ \eqref{fan-defined}.
\item Calculate the anomalous branching coefficients in the main Weyl
  chamber of the subalgebra $\mathfrak{a}$ using recurrent relation (\ref{recurrent-relation}).
\end{enumerate}
